### 2018-04-06 Manuscript/chapter4.tex
Materials and ch4 updates
Intro 2 para

\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background to data visualization}

\citealt{ped}
%\ref{sec:ggenealogy}
% \code{ggparcoord}
% \Figure \ref{fig:porcupine}

>>>>

\chapter{Gene expression responses to interactive stressors of diet quality and viral infection in \textit{Apis mellifera}}

\section{Introduction}

Commerically managed honeybees have undergone unusually large declines in the United States and parts of Europe over the past decade (\citealt{ccd1}, \citealt{ccd2}, \citealt{ccd3}), with annual mortality rates exceeding what beekeepers consider sustainable (\citealt{ccd5}, \citealt{ccd6}). More than 70 percent of major global food crops (including fruits, vegatables, and nuts) at least benefit from pollination, and yearly insect pollination services are valued wordwide at \$175 billion (\citealt{ccd7}). As honeybees are largely considered to be the leading pollinator of numerous crops, their marked loss has considerable implications regarding agricultural sustainability (\citealt{ccd4}).

Honeybee declines have been associated with several factors, including pesticide use, parasites, pathogens, habitat loss, and poor nutrition (\citealt{factors}, \citealt{factors2}). Researchers generally agree that these stressors do not act in isolation; instead, they appear to influence the large-scale loss of honeybees in interactive fashions as the environment changes (\citealt{interacting}). Two factors that have posed heightened danger to honeybee health related to environmental changes are nutrition and viruses.

\section{Methods}

\section{Results}

\section{Discussion}

% SYNTAX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\ref{sec:ggenealogy}
% \code{ggparcoord}
% \Figure \ref{fig:porcupine}
